### 2024-01-29 README.Rmd
update readme

```{bash eval=FALSE}
mamba deactivate 
cd mdtools
poetry shell
cd ../
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/TrailCamStorage_2" \
  -i "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats/TrailCamStorage_2" \
  -o "/workspace/rofcamtrap/2_LabelStudio/0_inputs/TrailCamStorage_2" \
  repeat-convert
```

@@

```{bash eval=FALSE}
docker exec -it label-studio-app-1 bash
curl -X GET http://localhost:8080/api/projects/?page_size=1000 -H 'Authorization: Token 3135fdd1f4a5b9b3630b69011ec4d70e7800c41d' -o files/outputs/project_counts.json
```

@@

```{bash eval=FALSE}
ls data/outputs/ls # 81 Jan 11 2024
```

>>>>

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/TrailCamStorage_2" \
  -i "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats/TrailCamStorage_2" \
  -o "/workspace/rofcamtrap/2_LabelStudio/0_inputs/TrailCamStorage_2" \
  repeat-convert
```

@@

```{bash eval=FALSE}
docker exec -it label-studio-app-1 bash
curl -X GET http://localhost:8080/api/projects/?page_size=1000 -H 'Authorization: Token INSERT_TOKEN' -o files/outputs/project_counts.json
```

@@

```{bash eval=FALSE}
ls data/outputs/ls # 82 Jan 29 2024
```
